Person with advantage functionality for `hyper3` objects: `pwa3()`

### 2025-12-06 inst/pwa3.Rmd
better example

To cite the `hyper2` package in publications, please use @hankin2017_rmd.

```{r definelamf}
lam <- function(lambda){
  race_nohelp <-
    race(letters[c(1,2,4,3)]) + 
    race(letters[c(3,1,2,4)]) +
    race(letters[c(2,4,1,3)])

  race_help <- 
    race(letters[c(2,3,1,4)]) |> pwa3("b", lambda) + 
    race(letters[c(1,3,4,2)]) |> pwa3("b", lambda) +
    race(letters[c(3,2,1,4)]) |> pwa3("b", lambda)

@@

```{r calclamf, cache=TRUE}
l <- exp(seq(from=log(0.02), to=log(8), len=17))
like <- sapply(l,lam)
```

@@

```{r lamfminus2, cache=TRUE}
f <- function(l){lam(l) - optimal_sol$objective + 2}
lower <- uniroot(f, interval = c(0.01, 1))
upper <- uniroot(f, interval = c(1, 10))
```

@@

```{r plotlamf}
plot(log(l), like - optimal_sol$objective, type='b')
abline(h=c(0, -2))
abline(v = log(optimal_sol$maximum))
segments(x0 = log(c(lower$root, upper$root)), y0 = -2.25, y1 = -1.75)
```

>>>>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  Here we analyse some simple Plackett-Luce
observations, using `hyper3` likelihood functions.

Our observations are a total of six order statistics for four
competitors `a,b,c,d`.  These competitors race three times under
Plackett-Luce probabilities.  They then race three times, but with
competitor `b` having some advantage (steroids?), parametrized by his
Plackett-Luce strength being $\lambda b$.

Our object of inference is $\lambda$; the Plackett-Luce strengths
`a,b,c,d` are nuisance parameters.

```{r definelamf}
lam <- function(lambda){

  race_nohelp <-
    race(c("b","a","d","c")) + 
    race(c("c","b","a","d")) + 
    race(c("b","d","a","c"))

  race_help <- 
    race(c("a","c","d","b")) |> pwa3("b", lambda) + 
    race(c("c","d","b","a")) |> pwa3("b", lambda) + 
    race(c("d","c","a","b")) |> pwa3("b", lambda)

@@

Above we see that in the unaided case (the first three races), `b`
does quite well, coming first twice and second once.  In the aided
case, `b` does much worse, coming either third or fourth.  Evidently,
the "help" actually hinders `b` and we suspect that $\lambda<1$.

```{r calclamf, cache=TRUE}
l <- exp(seq(from=log(0.0002), to=log(2), len=7))
like <- sapply(l,lam)
```

@@

```{r lamfminus2, cache=TRUE}
f <- function(l){lam(l) - optimal_sol$objective + 2}
lower <- uniroot(f, interval = c(exp(-8), exp(-7)))
upper <- uniroot(f, interval = c(exp(-2), exp( 0)))
```

@@

```{r plotlamf, echo=TRUE,fig.cap="Log-likelihood function for lambda"}
plot(log(l), like - optimal_sol$objective, type='b')
abline(h = c(0, -2))
abline(v = log(optimal_sol$maximum))
abline(v = 0)
segments(x0 = log(c(lower$root, upper$root)), y0 = -2.25, y1 = -1.75, col='gray')
```

Figure \@ref(fig:plotlamf) shows
